A boundary-integral framework to simulate \\ the viscous erosion of a porous medium

### 2018-04-06 docs/methods/erosion_methods.tex
rearranged

Next, the computed shear stress is used to evolve the solid boundaries.
Tracking the interface of fluid-structure interaction problems with a long time horizon is particularly
difficult as the mesh can become distorted and tangled. 
Furthermore, the process of erosion naturally leads to regions of high curvature and even corners.
The interface tracking issues are addressed in two ways: first, we introduce a tangential velocity that keeps the grid equispaced with respect to arc length but that does not affect the interface dynamics; second, we introduce a curvature-penalizing term into the normal interface velocity to suppress high-frequency oscillations associated with nearly singular curvature.
Furthermore, the interface is parametrized in the so-called {\thL} coordinate-system so that the curvature penalization appears as a diffusive term that can easily be handled in a numerically stable fashion with an exponential integrator.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions\label{s:conclusions}}
We have developed a numerical framework for simulating two-dimensional
Stokesian erosion in a porous media.  By using a BIE formulation of the
fluid equations and a {\thL}, we achieve spectral accuracy

>>>>

Next, the computed shear stress is used to evolve the solid boundaries.
Tracking the interface of fluid-structure interaction problems with a long time horizon is particularly
difficult as the mesh can become distorted and tangled. 
Furthermore, the process of erosion naturally leads to regions of high curvature and even corners.
The interface tracking issues are addressed in two ways: first, we introduce a tangential velocity that keeps the grid equispaced with respect to arc length but that does not affect the interface dynamics; second, we introduce a curvature-penalizing term into the normal interface velocity to suppress high-frequency oscillations associated with nearly singular curvature.
Furthermore, the interface is parametrized in the so-called {\thL} coordinate system so that the curvature penalization appears as a diffusive term that can easily be handled in a numerically stable fashion with an exponential integrator.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions\label{s:conclusions}}
We have developed a numerical framework for simulating two-dimensional
Stokesian erosion in a porous media.  By using a BIE formulation of the
fluid equations and a {\thL}, we achieve spectral accuracy in space and
second-order accuracy in time.  In addition, the non-negligible
interactions between different bodies are accurately resolved.
